BIP-Predictor

### 2025-05-20 Sweave/BIP_predictor.Rnw
up

# Load the relevant M-SSA functionalities
# M-SSA functions
source(paste(getwd(),"/R/functions_MSSA.r",sep=""))
# Load signal extraction functions used for JBCY paper (relies on mFilter)
source(paste(getwd(),"/R/HP_JBCY_functions.r",sep=""))
# Utility functions for M-SSA, see tutorial 
source(paste(getwd(),"/R/M_SSA_utility_functions.r",sep=""))
source(paste(getwd(),"/R/M_SSA_paper_functions.r",sep=""))

>>>>

# Load the relevant M-SSA functionalities
# M-SSA functions
source(paste(getwd(),"/R/functions_MSSA.r",sep=""))
# Load signal extraction functions used for JBCY paper (relies on mFilter)
source(paste(getwd(),"/R/HP_JBCY_functions.r",sep=""))
# Utility functions for M-SSA, see tutorial 
source(paste(getwd(),"/R/M_SSA_utility_functions.r",sep=""))
source(paste(getwd(),"/R/M_SSA_paper_functions.r",sep=""))
# ROC curve: plots, AUC
source(paste(getwd(),"/R/ROCplots.r",sep=""))
